Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-08 FDT2020/main-section.tex
A few edits

Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$.  From the above discussion, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$. The spanning-tree polytope is integral so there are polynomial-time algorithms to construct this decomposition (See Proposition~\ref{cara} and surrounding discussion).

Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$. Consider the incidence vectors of feasible $O_i$-joins. Let $S$ be any subset of vertices with an even number of odd-degree vertices.  The $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices. The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the vertices.  Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
That is, $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
%\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}

>>>>

Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$.  From the above discussion, we can write
\begin{equation}
\label{eq:tree-decomp}
\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i},
\end{equation}
where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$. The spanning-tree polytope is integral so there are polynomial-time algorithms to construct this decomposition (See Proposition~\ref{cara} and surrounding discussion).

Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$.
%Consider the incidence vectors of feasible $O_i$-joins.
Let $S$ be any subset of vertices with an even number of odd-degree vertices.  The $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices. The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the vertices.  Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
That is, $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
%\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
